Differentially Private Bayesian Inference

### 2018-04-10 main.tex
fix bugs

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
& \leq \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
exp(\frac{\epsilon \hat{s}}{2 S(x)})
& \leq exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
\frac{\epsilon \hat{s}}{2 S(x)}
& \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
\hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
(1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
\end{split}
\end{equation*}

To proof this, we discuss some cases:

The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two event that $G=\{\lambda < 0\}$, and $\overline{G} = \{\lambda > 0\}$:

@@

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.
	\item $\lambda > 0$
	% \begin{itemize}
	% 	% \item $u(r) > 0$

@@

	% 	% \item $u(r) < 0$

	% 	% This need to be discuss further.
	% 	% We can have:
	% 	% \begin{equation*}
	% 	% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
	% 	% \end{equation*}

	% \end{itemize}
	% \end{itemize}
\end{itemize}

% In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.

In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, so we only need to consider the case $u(r) \leq 0$.

Because $\hat{s} = u(r)$ where $r \thicksim \expomech$, we can substitute $\hat{s}$ with $u(\expomech)$. Then, what we need to proof under the event $G = \{\lambda > 0, u(r) \leq 0\}$ is:
\begin{equation*}
u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
\end{equation*}
By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with:
\begin{equation*}
\begin{split}
Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
\end{split}
\end{equation*}
In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
\begin{equation*}
\begin{split}
Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
\end{split}
\end{equation*}

@@

% So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.

>>>>

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
&  \leq e^{\frac{\epsilon}{2}} \cdot \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
exp(\frac{\epsilon \hat{s}}{2 S(x)})
& \leq e^{\frac{\epsilon}{2}} \cdot exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
\frac{\epsilon \hat{s}}{2 S(x)}
& \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
\hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
(1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
\end{split}
\end{equation*}

To proof this, we consider some cases:

The sensitivity is always greater than 0, and we are using $-\hlg(\bysinfer(x),r)$ for utility function, i.e., $u(r) \leq 0$, we need to consider two cases that $\lambda < 0$, and $\lambda > 0$:

@@

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		\end{equation*}
	\item $\lambda > 0$
	% \begin{itemize}
	% 	% \item $u(r) > 0$

@@

	% 	% \item $u(r) < 0$
	% 	% This need to be discuss further.
	% 	% We can have:
	% 	% \begin{equation*}
	% 	% \lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
	% 	% \end{equation*}
	% \end{itemize}
	% \end{itemize}
% In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.

% In our case, we are using $-\hlg(\bysinfer(x),r)$ for utility function, so we only need to consider the case $u(r) \leq 0$.

Because $\hat{s} = u(r)$ where $r \thicksim \expomech$, we can substitute $\hat{s}$ with $u(\expomech)$. Then, what we need to proof under the case $\lambda > 0$ is:
\begin{equation*}
u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
\end{equation*}
By applying the accuracy property of exponential mechanism, we bound the probability that the equation holds with probability:
\begin{equation*}
\begin{split}
Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))}{|\mathcal{R}_{OPT}| exp(\epsilon OPT_{u(x)}/2 S(x))}\\
\end{split}
\end{equation*}

In our Bayesian Inference mechanism, the size of the candidate set $\mathcal{R}$ is equal to the size of observed data set plus 1, i.e., $n + 1$, and $OPT_{u(x)} = 0$, then we have:
\begin{equation*}
\begin{split}
Pr[u(\expomech) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
\end{split}
\end{equation*}

@@

\end{itemize}
% So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.
